DSCI-445 Project

### 2021-11-27 FinalProject445.Rmd
Added Librarys
--

```{r}
plot(cars)
```

Add a new chunk by clicking the *Insert Chunk* button on the toolbar or by pressing *Ctrl+Alt+I*.

When you save the notebook, an HTML file containing the code and output will be saved alongside it (click the *Preview* button or press *Ctrl+Shift+K* to preview the HTML file).

The preview shows you a rendered HTML copy of the contents of the editor. Consequently, unlike *Knit*, *Preview* does not run any R code chunks. Instead, the output of the chunk when it was last run in the editor is displayed.

>>>>

```{r}
set.seed(445)
library(leaps)
library(ISLR)
library(tidyverse) 
library(knitr)
library(glmnet) # package for lasso and ridge regression
library(pls)
library(ISLR)
library(ggpubr)
library(MASS)
library(splines)
library(gam)
library(tree)
library(randomForest)
library(gbm)
library(caret)
```
